Draft

### 2020-08-04 Draft.Rmd
draft paragraph changes (all of them) and correct the notation for HAR model error term

```{r, message=FALSE}
library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

As an alternative to likelihood-based prediction, scoring rules have been introduced before to produce and evaluate probabilistic forecasts. A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity (Gneiting & Raftery, 2007). Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al. (2020) and (ref 5). Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by (ref 1) captures our attention since its ‘focusing’ feature shows great values in financial risk management. In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.

@@

Scoring rules can be used in both estimation and prediction. In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$. That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$. $\hat \theta \to \theta$ as $n \to \infty$ under asymptotic situations. While in prediction, scoring rules assign a numerical value to density forecasts, addressing both sharpness and calibration. For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates. A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity. Forecasts candidates are often compared by their average scores. Therefore, the crucial importance of the propreity of scoring rules must be emphasized.Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and it is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q. P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) means the expected value of S(P,$\cdot$) under Q (Gneiting & Raftery, 2007).

Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL is used for focusing on a certain region(s) of densities.

The logarithmic score is defined as (1) where $p_t$ is the density forecasts. It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007). 
\begin{align}
S_{LS}(p_t, y_{t+1}) = log[p_t(y_{t+1})]
\end{align}
However, logarithmic score is criticized by its unboundness and its local property. Its useness is also questioned in (Bernardo, 1979), since he shows that every proper scoring rule is equivalent to logarithmic score. Gneiting & Raftery, (2007) argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized one. Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events. 
\begin{align}
CRPS(P,x)=-\int_{-\infty}^{\infty}(P(y)-I(y\geq x))^2dy
\end{align}
The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
\begin{align}
CRPS(N,x)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x-\mu}{\sigma})-\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
where $\phi$ and $\Phi$ are the probability density function and cumulative density function of the Gaussian predictive distribution.

Continuously ranked probability score is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented score for convenient comparison among scoring rules as shown in (4). 
\begin{align}
CRPS^*(N,x)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x-\mu}{\sigma})+\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
Both logarithmic score and continuously ranked probability score are used for producing and evaluating the entire predictive density. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose a new proper scoring rule, censored likelihood score, which allows users to assess the forecasts only in the interested region(s) instead of using weights to emphasize a particular part of the entire density forecast. It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
\begin{align}
S_{CSL}(p_t, y_{t+1})=I(y_{t+1} \in A_t)log[ p_t(y_{t+1})]+I(y_{t+1} \in A_t^c)log[\int_{A_t^c} p_t(s)ds]
\end{align}
[ref 5] prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on logarithmic score and continuously ranked probability score.

## 2.2 Illustration example 
### 2.2.1 Simulation overview

Density forecasts provide more complete information of uncertainty of a prediction than point and interval forecasts. Moreover, the tails of a density have a great importance in finance. It forms the foundation of risk management, such as Value-at-Risk (VaR), and asset allocation. It can also be used in derivatives pricing. (reference ?) --- find some papers.

[ref 5] provide empirical results showing that using censored likelihood score can improve 99% Value-at-Risk estimation. Moreover, Loaiza-Maya, Martin & Frazier, (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score. Their results show that Focused Bayes outperform exact Bayes which is using logarithmic score for updating the prior probability. Their work also points out the degree of model misspecification play a role in the performance of Focused Bayes.

Loaiza-Maya et al., (2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample. A predictive probability distribution is said to be optimal if it is optimal based on a user-specified scoring rule, not generally speaking.

Building on the previous research in this field, we conduct a numerical analysis first in section 2.2.2 and 2.2.3 to further investigate the effects of the form and degree of model misspecification on optimal forecast performance using data simulated from the (generalized) autoregressive conditional heteroscedasticity ((G)ARCH) and copula models.

### 2.2.2 Simulation design

In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimic the behavior of financial returns and volatility. Specifically, GARCH models can capture the volatility clustering and serial dependence, and the negative marginal skewness will be introducted using an inversion copula with degree of skewness controlled by the shape parameter showed below. In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^0.5 * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

@@

The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively. The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted. We conduct each simulation scenario as follows (Loaiza-Maya et al., 2020):

@@

\begin{align}
{\hat \theta^{[i]}}:=arg\max_{\theta \in \Theta}\bar S_i({\theta})
\end{align}

\begin{align}
\bar S_i(\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\theta}^{t-1},y_t)
\end{align}

  3.	Produce the one-step-ahead predictive $P^{t-1}_{\hat \theta_1^{[i]}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (8)(9)(10):

\begin{align}
S_{LS}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)
\end{align}

\begin{align}
S_{CRPS}^*(P_\theta^{t-1},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\theta)-I(y \geq y_t)]^2dy
\end{align}

\begin{align}
S_{FSR}(P_\theta^{t-1},y_t)=lnp(y_t|\mathcal{F}_{t-1},\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\theta)dy}]I(y_t \in A^c)
\end{align}

4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{align}
\bar S_j(\hat \theta^{[i]})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\hat \theta^{[i]}}^{t-1},y_t)
\end{align}

### 2.2.3 Simulation results
#### 2.2.3.1 Average score tables

Loaiza-Maya et al., (2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance. Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence is when the optimal prediction is strictly preferable given that score. Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on $S_1, S_2$, then the prediction is said to coherent if 
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
\end{align}

\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
\end{align}

It is said to be strictly coherent if the equality doesn't hold in (11)(12).

\textbf{[need to mention some results from opt paper - one sentence]}

The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation. The bolded value(s) is the maximum(s) in each column. We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the score indicated by the column name.

@@

From Table 3. we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case. These results are consistent with conclusions from (Loiaza-Maya et al., 2020). It simply means that we can improve prediction accuracy in the presence of model misspecification ?? , and gain more from using optimal forecasts method while the degree of model misspecification is high. In other words, we are expected to gain more from using focused score when we observe 'strict coherence' while comparing two forecasts.

@@

\textbf{[need copula paper citation here to explain more]}

@@

#### 2.2.3.2 Score traces plots

As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails. Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2. In the left panel, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From figure 1 and 2, we could see that FSR makes no difference if the degree of model misspecification is very small but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model in the fact that in practice, a correct model does not exist.

@@

Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots. They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and therefore, outperform predictions from using LS.

@@

The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a time period that precedes the 2008 Global financial crisis (GFC) and extends to the latest period in which COVID-19 has impacts on financial market. The methodology used here is the same as in the section 2.2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered") %>% 
  add_header_above(c("Table ?: Descriptive statistics"=9))
```

@@

The descriptive statistics shows that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation. Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.

The reality is always the most complicated and the underlying ARCH(1) should have a high degree of model misspecification. Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution. The results of Table 9 support our conjecture. However, the difference between using FSR10(80) and FSR20(90) is very small.

@@

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 9: Average scores for S&P500"=7))
```

Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some important events. In figure 12, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE in terms of predicting both upper and lower tails. And this 'jump' effect continues until the very recent date. It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.

@@

@@

Value-at-Risk (VaR) is a commonly used risk measurement in finance. It can be obtained from a probability density function of returns over a chosen investment horizon. It is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
\begin{align}
VaR = -q_p \\p=1-\alpha
\end{align}
It indicates that investors will not lose more than the amount as shown in VaR. It represents the worst level of the investments with $\alpha$ confidence level. There are different methods to estimate VaR, but it is clear that predictive density plays an important role here. Therefore, a more accurate prediction can contribute to improving the accuracy of VaR estimation.

[ref 5] conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.

We implement VaR analysis by using VaR backtesting method. It evaluates the prediction accuracy with the proportion of exceedances ($y_t < VaR_t$). That is, an accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%. We illustrate how optimal forecasts perform in estimating VaR by using simulation data from section 2 first and expect outperformance of focused scoring rules.

@@

figure <- ggarrange(p1,                                                 
          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
          nrow = 2, 
          labels = "A"                                        
          ) 
annotate_figure(figure, 
                top = text_grob("Descriptive figures",face = "bold"),
                fig.lab = "Figure 13",fig.lab.face = "bold"
                )
```

>>>>

```{r, message=FALSE}
# library(formattable)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(tsibbledata)
library(feasts)
library(normtest)
library(moments)
library(ggthemes)
library(ggpubr)
library(knitr)
library(kableExtra)
```

@@

As an alternative to likelihood-based prediction, scoring rules have been introduced before to produce and evaluate probabilistic forecasts. A variety of proper scoring rules allows users to produce probability predictions based on their interests, and to compare these predictions, as long as they refer to the same forecast quantity (Gneiting & Raftery, 2007). Some recent and previous researches show that forecasts produced based on a given scoring rule can be improved for both Bayesian and frequentist prediction, even in the presence of model misspecification; see Loaiza-Maya, Martin & Frazier (2019), Loaiza-Maya et al. (2020) and Opschoor, van Dijk & van der Wel (2017). Among all these, censored likelihood score (CSL) or focused score (FSR) proposed by Diks, Panchenko & van Dijk (2011), captures our attention since its ‘focusing’ feature shows great values in financial risk management. In other words, CSL/FSR allows a forecaster to focus on predicting any region of his/her interests more accurately and therefore, it is expected to make great contributions to risk estimation in finance.

@@

Scoring rules can be used in both estimation and prediction. In estimation, an optimum estimator $\hat \theta$ can be obtained by maximizing a scoring rule $S_n$ on the condition that $S_n$ is positively oriented. That is, $\hat \theta_n=arg \max_\theta S_n(\theta)$, $\hat \theta \to \theta$ as $n \to \infty$. While in prediction, scoring rules assign a numerical value to density forecasts, simultaneously addressing both sharpness and calibration (Gneiting & Reftery, 2007). For a positively oriented score, higher value will be assigned to a better forecast between two competing candidates. The crucial importance of the propreity of scoring rules must be emphasized for the purpose of ranking and comparing forecasts based on scoring rules. Gneiting & Raftery, (2007) illustrate the importance of propreity via a case study in weather forecasts and point out that improper scoring rules will assign higher average score to an incorrect density forecast and consequently, mess up the prediction evaluation. Suppose P and Q are predictive distributions and Q is the best forecast given all the available information. S(P,Q) denotes the expected value of S(P,$\cdot$) under Q. A scoring rule is said to be proper if $S(Q,Q) \geq S(P,Q)$ for all P and Q, and is strictly proper if $S(Q,Q) = S(P,Q)$ only happens when P = Q (Gneiting & Raftery, 2007).

Some commonly used proper scoring rules are the logarithmic score (LS), the continuously ranked probability score (CRPS) and censored likelihood score (CSL) or focused score (FSR) in a sense that CSL focuses on predicting a certain region(s) of densities.

The logarithmic score is defined as (1) where $p_t$ is the probabilistic density forecast. It is a local strictly proper scoring rule, which means it will assign a higher score to the correct probabilistic forecast, and it is superior to quadratic and spherical scoring rules when the rank ordering is important or the impact of nonlinear utility function used is a concern for forecasters (Bickel, 2007). 
\begin{align}
S_{LS}(p_t, y_{t+1}) = log[p_t(y_{t+1})]
\end{align}
However, logarithmic score is criticized by its unboundness and its local property. Bernardo (1979) states "locality requires the utility of probabilistic influence to depend only upon the probability density of the true state". Gneiting & Raftery (2007) also argue that logarithmic score is insensitive to distance and will not reward predictions that are close to but not identical to the materialized event. Therefore, Gneiting & Raftery, (2007) propose the continuously ranked probability score, which is sensitive to distance and is defined as in (2) where P is the cumulative distriubtion function, I is the indication function, and x is the materialized events. 
\begin{align}
CRPS(P,x)=-\int_{-\infty}^{\infty}(P(y)-I(y\geq x))^2dy
\end{align}
The formula can be simplifed to (3) if the prediction distribution is Gaussian with mean = $\mu$ and variance = $\sigma^2$.
\begin{align}
CRPS(N,x)=\sigma[\frac{1}{\sqrt{\pi}}-2\phi(\frac{x-\mu}{\sigma})-\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
where $\phi$ and $\Phi$ are the probability density function and cumulative density function of the Gaussian predictive distribution.

CRPS is defined as a negatively oriented scoring rule, but it can be easily transformed to positively oriented form as shown in (4) for convenient comparison among scoring rules in following sections. 
\begin{align}
CRPS^*(N,x)=\sigma[-\frac{1}{\sqrt{\pi}}+2\phi(\frac{x-\mu}{\sigma})+\frac{x-\mu}{\sigma}(2\Phi(\frac{x-\mu}{\sigma})-1)]
\end{align}
Both LS and CRPS are used for producing and evaluating the entire predictive density. In terms of accurately predicting a certain region of a distribution, they are typically used together with weighted likelihood (Gneiting & Ranjan, 2011). Diks, Panchenko & van Dijk, (2011) propose a new proper scoring rule, censored likelihood score, which allows users to assess the forecasts only in the interested region(s) instead of using weights to emphasize a particular part of the entire density forecast. It is defined as in (5) where $p_t$ is the predictive probability density function, $A_t$ is the interested region(s) and $A_t^c$ is the complement of $A_t$.
\begin{align}
S_{CSL}(p_t, y_{t+1})=I(y_{t+1} \in A_t)log[ p_t(y_{t+1})]+I(y_{t+1} \in A_t^c)log[\int_{A_t^c} p_t(s)ds]
\end{align}
Opschoor, van Dijk & van der Wel (2017) prove that weighted density forecasts based on optimizing the censored likelihood score outperform those on LS and CRPS.

## 2.2 Numerical investigation
### 2.2.1 Simulation design

Loaiza-Maya, Martin & Frazier (2019) propose a new method, Focused Bayes, in Bayeisian prediction by replacing the conventional likelihood function with the censored likelihood score. In their simulated and empirical analysis, Focused Bayes outperforms exact Bayes which is using logarithmic score for updating the prior probability and they also point out the model misspecification plays a role in the performance of Focused Bayes since focusing incorrectly can harm.

Loaiza-Maya et al.(2020) extend the above discussion to frequentist probability forecasting. They address questions about when we can/cannot benefit from optimal probabilistic forecasts out of sample. Loaiza-Maya et al.(2020) introduce the concepts of ‘coherence’ and ‘strict coherence’ for conveniently documenting the optimal forecasts’ performance. Coherence means when the optimal probabilistic forecast based on a given score is superior, or at least performs the same as, alternative forecasts according to the same score. Strict coherence is when the optimal prediction is strictly preferable given that score. Let $\boldsymbol{\hat \theta}_1$ and $\boldsymbol{\hat \theta}_2$ be the optimizers based on scoring rules: $S_1, S_2$, then the prediction is said to be coherent if 
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \geq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_1(P^{t-1}_{\boldsymbol{\hat \theta_2}},y_t)
\end{align}
\begin{align}
\frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t) \leq \frac{1}{\tau}\sum_{t=T-\tau+1}^{T}S_2(P^{t-1}_{\boldsymbol{\hat \theta_1}},y_t)
\end{align}
It is said to be strictly coherent if the equality doesn't hold in (6)(7).

Building on the previous research in this field, we conduct a numerical analysis first in this sub section to further investigate the effects of the form and degree of model misspecification on optimal forecast performance. In order to prepare the financial application analysis in following sections of this paper, we simulate a time series dependnet variable $y_t$ that mimics the behavior of financial returns and volatility. Specifically, GARCH models are used to capture the volatility clustering and serial dependence usually observed in empirical stock return's distribution, and the negative marginal skewness will be incorporated by an inversion copula with degree of skewness controlled by the shape parameter. In order to manipulate the degree and form of model misspecification, we fix the underlying model to a simple and clearly misspecified ARCH(1) model.

@@

\begin{table}[!h]
\centering
\begin{tabular}{|c|c|c|}
\hline
\multicolumn{3}{|c|}{\textbf{Simulation design}} \\ \hline
          & \textbf{Scenario (i)} & \textbf{Scenario (ii)} \\ \hline
\textbf{True DGP} & $y_t = \sigma_t \epsilon_t$ & copula \\
& $\sigma_t^2 = 1 + 0.2y_{t-1}^2+0.7\sigma_{t-1}^2$ & Shape parameter = {0, -3, -5}\\ & $\epsilon_t \sim (\frac{\nu-2}{\nu})^{0.5} * t_\nu$ & \\ & $\nu \in (3, 12, 10000)$ & \\ \hline

@@

The tails of density are important for risk management in finance so that we decide to apply focused scoring rule (FSR) to 10%, 20%, 80% and 90% tails of the distribution, corresponding to short and long portfolios in finance respectively. The methodology in Loaiza-Maya et al., (2020) and Loaiza-Maya, Martin & Frazier, (2019) is adopted here. We conduct each simulation scenario as follows:

@@

\begin{align}
\boldsymbol{{\hat \theta}^{[i]}}:=arg\max_{\boldsymbol{\theta \in \Theta}}\bar S_i({\boldsymbol\theta})
\end{align}
\begin{align}
\bar S_i(\boldsymbol\theta):=\frac{1}{T-(\tau+1)}\sum^{T-\tau}_{t=2}S(P_{\boldsymbol\theta}^{t-1},y_t)
\end{align}
  3.	Produce the one-step-ahead predictive $P^{t-1}_{\boldsymbol{\hat \theta_1^{[i]}}}$ And compute the out-of-sample score using $S_j$, where $S_i$ and $S_j$ refer to (10)(11)(12):

\begin{align}
S_{LS}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)
\end{align}
\begin{align}
S_{CRPS}^*(P_{\boldsymbol\theta^{t-1}},y_t)=\int^{+\infty}_{-\infty}[P(y|\mathcal{F}_{t-1},\boldsymbol\theta)-I(y \geq y_t)]^2dy
\end{align}
\begin{align}
S_{FSR}(P_{\boldsymbol\theta^{t-1}},y_t)=lnp(y_t|\mathcal{F}_{t-1},\boldsymbol\theta)I(y_t \in A)+[ln\int_{A^c}{p(y|\mathcal{F}_{t-1},\boldsymbol\theta)dy}]I(y_t \in A^c)
\end{align}
4. Expand estimation window by one observation and repeat step 2-3 with $\tau = T-1000$ times and compute the average scores: 
\begin{align}
\bar S_j(\boldsymbol{\hat \theta^{[i]}})=\frac{1}{\tau}\sum^T_{t=T-\tau+1}S_j(P_{\boldsymbol{\hat \theta^{[i]}}}^{t-1},y_t)
\end{align}

### 2.2.2 Simulation results
#### 2.2.2.1 Average score tables

The first column of following tables shows $S_i$ that we used to produce predictions and the first row shows $S_j$, which is used for forecasts evaluation. The bolded value(s) is the maximum(s) of $\bar S_j(\boldsymbol{\hat \theta^{[i]}})$ in each column. We use all positively oriented scoring rules, and therefore, the column maximum(s) indicate(s) the optimal prediction(s) based on the evaluating scoring rule indicated by the column name.

@@

@@

From Table 3. we could observe strict coherence when degree of model misspecification is high and coherence in Table 1 which is stated as correct specification case. These results are consistent with conclusions from Loiaza-Maya et al.(2020). It simply means that we can improve prediction accuracy by using FSR in the presence of model misspecification under certain conditions. That is, we are expected to gain more from optimal forecasts while the degree of model misspecification is high.

@@

#### 2.2.2.2 Score traces plots

As stated in previous literature, focused score tends to outperform CRPS and logarithmic score in predicting tails. Therefore, we provide score trace plots to exhibit the comparison of LS, CRPS and FSR’s performance in predicting the 10 percentile and 90 percentile in figure 1 and 2. In the left panel, it shows the performance of each score evaluated by FSR 10%. That is, if the average score value of score A used for estimation is higher than score B, then score A predicts the 10 percentile of the distribution more accurately than score B. The right panel shows the same thing but is based on performance of predicting 90 percentile. From figure 1 and 2, we could see that FSR almost makes no difference if the degree of model misspecification is very small compared with other scoring rules, but as it increases, FSR starts to outperform CRPS and MLE (LS) in predicting tails. The more misspecified the model is, the more benefits can we gain from using FSR. It is beneficial for econometricians to improve forecast accuracy without working so hard on finding a ‘correct’ model when in practice, a correct model does not exist.

@@

Moreover, the predictive density plots (Appendix 1) in figure 3 to 8, further support our conclusions drawn from the average score tables and score trace plots in above sections. They show that predictions obtained from optimizing focused scores aim to match the shape of tails of the true distribution and the changes over time/iterations.

@@

The data used in the analysis is the continuously compounded daily log returns of S&P500 listed in U.S.A financial market over a broad time period from 27 Sep,1996 to 30 July,2020. It aims to include two very volatile periods, 2008 Global financial crisis (GFC) and the recent COVID-19 pandemic. The methodology used here is the same as in the section 2.2 with initial training sample size set to be 1000 and 5000 out-of-sample observations.

@@

```{r}
sum <- data.frame(Stock="S&P500",Min=as.numeric(summary[1]),Median=as.numeric(summary[3]),Mean=as.numeric(summary[4]),Max=as.numeric(summary[5]),Skewness=sk,Kurtosis=kt,JB.Test=28270,LB.Test=61.489)
sum %>% 
  kable("latex",booktabs = T) %>% 
  kable_styling("bordered") %>% 
  add_header_above(c("Table 7: Descriptive statistics"=9))
```

@@

figure <- ggarrange(p1,                                                 
          ggarrange(p2, p3, ncol = 2, labels = c("B", "C")), 
          nrow = 2, 
          labels = "A"                                        
          ) 
annotate_figure(figure, 
                top = text_grob("Descriptive figures",face = "bold"),
                fig.lab = "Figure 9",fig.lab.face = "bold"
                )
```

The descriptive statistics show that the distribution of S&P500 log returns are negatively skewed and have fat tails and strong serial correlation in its volatility. Besides, during the GFC and COVID-19 pandemic periods, the volatility is very high due to high uncertainty.

We still use ARCH(1) model in section 2.2 as the assumed predictive model since it is a reasonable model to predict stock returns and volatility and more importantly, it is misspecified with a high degree of model misspecification. Therefore, we should expect that predictions produced by optimizing FSR do a better job in predicting two tails of the distribution. The results of Table 8 support our conjecture. However, the difference between using FSR10(80) and FSR20(90) is very small.

@@

sp_table %>% 
  mutate(
    LS = cell_spec(format(LS,4),"latex",bold = ifelse(LS == max(LS),TRUE,FALSE)),
    CRPS = cell_spec(format(CRPS,4),"latex",bold = ifelse(CRPS==max(CRPS),TRUE,FALSE)),
    `FSR10` = cell_spec(format(`FSR10`,4),"latex",bold = ifelse(`FSR10`==max(`FSR10`),TRUE,FALSE)),
    `FSR20` = cell_spec(format(`FSR20`,4),"latex",bold = ifelse(`FSR20`==max(`FSR20`),TRUE,FALSE)),
    `FSR80` = cell_spec(format(`FSR80`,4),"latex",bold = ifelse(`FSR80`==max(`FSR80`),TRUE,FALSE)),
    `FSR90` = cell_spec(format(`FSR90`,4),"latex",bold = ifelse(`FSR90`==max(`FSR90`),TRUE,FALSE))
  ) %>%
  kable("latex",escape = F, booktabs = T, linesep = "") %>%
  kable_styling("bordered",full_width = F)%>%
  add_header_above(c("","Average out-of-sample scores"=6)) %>% 
  add_header_above(c("Table 8: Average scores for S&P500"=7))
```

Unlike simulation, the score trace plots show how different scoring rules perform in real time points which correspond to some historical events. In figure 10, one interesting phenomenon is that after the GFC, focused score performs much better than CRPS and MLE compared with before, in terms of predicting both upper and lower tails. And this 'jump' effect continues until the very recent date. It indicates that optimal probabilistic forecasts might predict financial markets better in and after times of stock market turbulance, which could represent a great contribution to the existing financial analyses of risks and returns.

@@

# put two plots side by side 
ggarrange(fsr10plot,fsr90plot,ncol=2,legend = "bottom",labels = c("Figure 10(a) Lower Tail","Figure 10(b) Upper Tail"))

@@

Density forecasts have great practical values in finance. It forms the foundation of risk management, such as Value-at-Risk (VaR) and is useful for asset allocation and derivative pricing. VaR is a commonly used risk measurement in finance. It can be obtained from a probability density function of returns over a chosen investment horizon. It is the p-quantile of a predictive distribution of a portfolio’s profit/loss over a holding period, according to a given confidence interval $\alpha$ (Dowd, 2005).
\begin{align}
VaR = -q_p \\p=1-\alpha
\end{align}
It indicates that investors will not lose more than the amount as shown in VaR. It represents the worst level of the investments with the given $\alpha$ confidence level. There are different methods to estimate VaR, but it is clear that predictive density plays an important role here. Therefore, a more accurate prediction can contribute to improving the accuracy of VaR estimation.

Opschoor, van Dijk & van der Wel (2017) conduct combining density forecasts using focused scoring rules, and the results show weighted density forecasts based on optimizing the focused score outperform those based on optimizing CRPS or LS and improve the accuracy of 99% Value-at-Risk estimates.

We illustrate how optimal forecasts perform in estimating VaR by usig predictions produced in section 2.2 and 2.3 and expect optimal forecasts based on FSR would give us a better prediction in tails. We implement VaR analysis by using VaR backtesting method. Specifically, we follow the steps as bellow:

1. Using the predictive densities produced in section 2.2 and 2.3: $p(y_{1001}|y_{1000})...p(y_{5000}|y_{4999})$;

2. Construct the VaR at \{10%, 20%, 80%, 90%\} using predictive densities in step 1;

3. Compare the true values of $y_{1001}...y_{5000}$ with $VaR_t$ and calculate the proportion of exceedances ($y_t < VaR_t$); An accurate estimation of the p% VaR is observed if the proportion of exceedances equals to p%.

@@
